%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {Junior Software Engineer} % Job title
    {Foriba} % Organization
    {Maltepe/İstanbul} % Location
    {Jun. 2018 - } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed custom monitoring tool for Halkbank E-Invoice System. .NET Core backend with REST API and Angular as Frontend }
        \item {Developed custom operational tools for Halkbank E-Invoice System. .NET Core backend with REST API and Angular as Frontend}
        \item {Integrated to government E-Invoice web services.For sending and receiving E-Invoice.}
        \item {Developed custom interface for support team so that they able to response faster to customers.}
        \item {Implemented custom parser for XBRL datatype.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Technical Software Support} % Job title
    {Isis Bilişim Teknolojileri} % Organization
    {Maltepe/İstanbul} % Location
    {Mar. 2017 - June. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed monitoring and operational tools for big giant monolith system so we would know when we down. Java Spring Framework Backend/Thymleaf as Frontend}
        \item {Developed many special XSLT for customers for their E-Invoices.}        
        \item {Debugging for errors reported by customer and forward to software team with details.}        
        \item {Developed automatic web service tool so that we would know about errors after new relase. .NET Framework Windows Forms Application}
        \item {Manage database on promise system. Index and server maintaince.}
      \end{cvitems}
    }




%---------------------------------------------------------
  \cventry
    {Internship} % Job title
    {Pakmaya} % Organization
    {Cumayeri/Duzce} % Location
    {Jun. 2015 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Server Maintaining}
        \item {Pushing updates to come from central. }
        \item {Manage security policies}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Internship} % Job title
    {VTEL Telecom} % Organization
    {Levent/İstanbul} % Location
    {Jun. 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing VoIP server for clients.}
        \item {Implement custom VoIP software on custom circuit that attached to RaspberryPI}
        \item {Several bugfixes and frontend development done by me.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Finish Project(Web Controlled Smart Home System)} % Job title
    {Kocaeli University} % Organization
    {İzmit/Kocaeli} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented PHP backend for sending messages to arduino via MQTT broker.}
        \item {Developed Arduino for sending and receiving messages via MQTT broker.}
        \item {Made RC Tank that controllable from internet.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Game Development Class} % Job title
    {Kocaeli University} % Organization
    {İzmit/Kocaeli} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed game like Space Invaders. Enemy has smart guns that follows you and Able to predict your movements.}
        \item {Development done in Unity. https://github.com/wiyyyy/SpacePatrol }
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
